DeepSphere: a graph-based spherical CNN

### 2019-11-14 main.tex
small modifications
update

% 2) explain our approach
We chose a different approach and take inspiration from \citet{belkin2005towards}, which proves that for a random \emph{uniform sampling} scheme the graph Laplacian converges toward the Laplace-Beltrami operator $\Delta_{\mathbb{S}^2}$ as the number of sampling points goes to infinity.
This convergence result is important as a) $\Delta_{\mathbb{S}^2}$ commutes with rotation ($\Delta_{\mathbb{S}^2}R(g) = R(g)\Delta_{\mathbb{S}^2}$) and b) is diagonalized by the spherical harmonics.
In this case the weighting scheme is full (every node is connected to every node) and is based on the exponential kernel:
\begin{equation} \label{eqn:weights:belkin}
w_{ij} = e^{-\frac{1}{4t} \norm{x_i-x_j}^2}
\end{equation}
In practice, because of the exponential, most of the weights are very close to $0$. Hence, to optimize for computational efficiency, we limit ourselves to only the $k$ nearest neighbors.
Given $k$, the optimal $t$ is found by searching for the minimizer of \eqref{eq:mean equivariance error}.
\Figref{kernel_widths} shows the optimal kernel widths found for various resolutions of the HEALPix grid.

@@

		\caption{Normalized mean equivariance error \eqref{eq:mean equivariance error}. The number of pixels is $n = 4 s^2$ for the equiangular sampling and $n = 12 s^2$ for the HEALPix sampling.}
		\label{fig:equivariance_error}
	\end{minipage}
	\hfill
	\begin{minipage}{0.35\linewidth}
		\centering
		\includegraphics[width=\linewidth]{kernel_widths}
		\caption{Optimal kernel widths.}
		\label{fig:kernel_widths}
		\vspace{1em}
		\includegraphics[height=4.5em]{lamp_000018}
		\hfill
		\includegraphics[height=4.5em]{lamp_000018_sphere_nobar}
		\caption{3D object represented as a spherical depth map.}
		\label{fig:depthmap}
		\vspace{1em}
		\includegraphics[width=\linewidth]{spectrum}
		\caption{Power spectral densities.}
		\label{fig:spectrum}
	\end{minipage}
\end{figure}

>>>>

% 2) explain our approach
We chose a different approach and take inspiration from \citet{belkin2005towards}, which proves that for a random \emph{uniform sampling} scheme the graph Laplacian converges toward the Laplace-Beltrami operator $\Delta_{\mathbb{S}^2}$ as the number of sampling points goes to infinity.
This convergence result is important as a) $\Delta_{\mathbb{S}^2}$ commutes with rotation ($\Delta_{\mathbb{S}^2}R(g) = R(g)\Delta_{\mathbb{S}^2}$) and b) is diagonalized by the spherical harmonics.
In this case the weighting scheme is full (every node is connected to every node) and is based on the exponential kernel:
\begin{equation} \label{eqn:weights:belkin}
w_{ij} = e^{-\frac{1}{4t} \norm{x_i-x_j}^2}
\end{equation}
In practice, because of the exponential, most of the weights are very close to $0$. Hence, to optimize for computational efficiency, we limit ourselves to only a few neighbors.
In~\cite{perraudin2019deepspherecosmo}, each pixels is connected to their 8 adjacent pixels\footnote{It is slightly more complex than that and we invite the curious reader to read~\cite{perraudin2019deepspherecosmo}.} and the parameter $t$ was heuristically set to $0.5$ times the average squared distances over all connected pixels.
This heuristic however seems to over-estimate $t$ (see \Figref{kernel_widths}). 
In this work, we decided to use a more refined method.
Given the $k$ nearest neighbors, the optimal $t$ is found by searching for the minimizer of \eqref{eq:mean equivariance error}.
\Figref{kernel_widths} shows the optimal kernel widths found for various resolutions of the HEALPix grid. 
% We observe that using a small kernel size $t$, \cite{perraudin2019deepspherecosmo} would probably be more equivariant.

@@

		\caption{Normalized mean equivariance error \eqref{eq:mean equivariance error}. The number of pixels is $n = 4 s^2$ for the equiangular sampling and $n = 12 s^2$ for the HEALPix sampling.}
		\label{fig:equivariance_error}
	\end{minipage}
	\hfill
	\begin{minipage}{0.35\linewidth}
		\centering
		\includegraphics[width=\linewidth]{kernel_widths}
		\caption{Optimal kernel widths. For comparizon, we added the kernel widths used by~\cite{perraudin2019deepspherecosmo} (8 neighbors).}
		\label{fig:kernel_widths}
		\vspace{1em}
		\includegraphics[height=4.5em]{lamp_000018}
		\hfill
		\includegraphics[height=4.5em]{lamp_000018_sphere_nobar}
		\caption{3D object represented as a spherical depth map.}
		\label{fig:depthmap}
		\vspace{1em}
		\includegraphics[width=\linewidth]{spectrum}
		\caption{Power spectral densities.}
		\label{fig:spectrum}
	\end{minipage}
\end{figure}
